Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2015-01-07 windheat.tex
More changes to windheat appendix.

The energy and mass injection from stellar winds will be the sum ofthe
contributions from main sequence and post-main sequence (PMS) stars.
For an impulsively formed stellar population of age $t$, the mass
injection rate per unit stellar mass ($\dot{\bar{m}}(t)$) and energy
injection rate per unit stellar mass will be given by
($\dot{\bar{e}}(t)$).

@@

The first terms in each expression above correspond to the
contributions from PMS stars, while the second terms correspond to the
contributions from main sequence stars. The main sequence winds are
subdominant in mass, and may be not be thermalized and
mixed with the rest of the injected gas. Thus, we include a
thermalization efficiency, $ 0\le f_{\rm MS}\le 1$, in
equation~\eqref{eq:edotImp}. Throughout this paper we set $f_{\rm
  MS}=1$.

We assume a Salpeter IMF $\mu(\Mstar)\sim M^{-2.35}$, truncated at $0.1
\Msun$ on the low mass end and at $100 \Msun$ on the high mass
end. The corresponding $\bar{m}_*$ is 0.35 $\Msun$.

@@

To estimate the mass loss from main sequence stars $\dot{\Mstar,t}$,
we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This
  prescription is a generalization of the Reimers' mass loss law. This
expression is derived assuming the stellar wind results from the
turbulent overflow of moaterial in the chromosphere or underneath it.} {\bf AG:
  unfortunately this is not really meant for MS stars...}

>>>>

The energy and mass injection from stellar winds will be the sum ofthe
contributions from main sequence and post-main sequence (PMS) stars.
For an impulsively formed stellar population of age $t$, the mass
injection rate per unit stellar mass,$\dot{\bar{m}}(t)$, and  the energy
injection rate per unit stellar mass, $\dot{\bar{e}}(t)$,  will be given by

@@

The first terms in each expression above correspond to the
contributions from PMS stars, while the second terms correspond to the
contributions from main sequence stars. The main sequence winds are a
small fraction of the mass, and they may be not be thermalized and
mixed with the rest of the injected gas. Thus, we include a
thermalization efficiency, $ 0\le f_{\rm MS}\le 1$, in
equation~\eqref{eq:edotImp}. Throughout this paper we set $f_{\rm
  MS}=1$.

We assume a Salpeter IMF $\mu(\Mstar)\sim M^{-2.35}$, truncated at $0.1
\Msun$ on the low mass end and at $100 \Msun$ on the high mass
end. The corresponding mean stellar mass, $\bar{m}_*$ is 0.35 $\Msun$.

@@

To estimate the mass loss from main sequence stars
$\dot{m}(\Mstar, t)$,
we use equation 4 \citet{SchroderCuntz:2005a}\footnote{This
  prescription is a generalization of the Reimers' mass loss law. This
expression is derived assuming the stellar wind results from the
turbulent overflow of moaterial in the chromosphere or underneath it.} {\bf AG:
  unfortunately this is not really meant for MS stars...}
